---
title: "W241_Project_PGSS_Campaign"
author: "Subha Vadakkumkoor, Walter Burge"
date: "August 3, 2018"
output: pdf_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}
library(data.table)
library(stargazer)
library(dplyr)
library(readr)
```

## Loading data

Data imported from Salsa, excluding PII fields (name and email address) are read into R dataframes. All dataframes have the same structure and format. With each step of the treatment (Orignal email, Reminder1 and Reminder2), there are 2 files: list of people that were assigned the treatment (recieved the email) and list of people that responded to the treatment (donated money).


```{r}

#Load data

#Original email
orig_email_rec<-read.csv('./data/BlastReport_Class Experiment Final Email_Recipients.csv')
setnames(orig_email_rec, old=c("Opened"), new=c("opened_orig_email"))

orig_email_resp<-read.csv('./data/BlastReport_Class Experiment Final Email_Conversions.csv')
sapply(orig_email_resp, class)
#Create an indicator and rename columns to reflect original email response (useful for merge later)
orig_email_resp$donated_after_orig_email=1
names(orig_email_resp)
setnames(orig_email_resp, old=c("Conversion.Date","Amount"), new=c("Orig_email_conversion_date", "orig_email_amount"))

#Reminder1
reminder1_rec<-read.csv('./data/BlastReport_Class experiment Reminder1_Recipients.csv')
setnames(reminder1_rec, old=c("Opened"), new=c("opened_reminder1"))
reminder1_rec_subset=reminder1_rec[,c("opened_reminder1","Supporter.ID")]

reminder1_resp<-read.csv('./data/BlastReport_Class experiment Reminder1_Conversions.csv')
reminder1_resp$donated_after_reminder1=1
setnames(reminder1_resp, old=c("Conversion.Date","Amount"), new=c("reminder1_conversion_date", "reminder1_amount"))

#Reminder2
reminder2_rec<-read.csv('./data/BlastReport_Class Experiment Reminder 2_Recipients.csv')
setnames(reminder2_rec, old=c("Opened"), new=c("opened_reminder2"))
reminder2_rec_subset=reminder2_rec[,c("opened_reminder2","Supporter.ID")]


reminder2_resp<-read.csv('./data/BlastReport_Class Experiment Reminder 2_Conversions.csv')
reminder2_resp$donated_after_reminder2=1
setnames(reminder2_resp, old=c("Conversion.Date","Amount"), new=c("reminder2_conversion_date", "reminder2_amount"))

#Load donor profile file
alumni_profile<-read.csv('./data/Alumni_profile_all.csv',colClasses = c("character","character","numeric","character","character","character","character","character","character","character","character","numeric","numeric","numeric","numeric","numeric","numeric","numeric"), na.strings=c('','  ','   '))
sapply(alumni_profile,class)
#names(alumni_profile)

#Examine the layout of a representative file
cat("Fields in recipients file\n")
#names(orig_email_rec)

cat("\nFields in responder files\n")
#names(orig_email_resp)

#Get dimensions of each file
cat("\nDimensions of each file\n")
dfList <- list(orig_email_rec,orig_email_resp,reminder1_rec,reminder1_resp,reminder2_rec,reminder2_resp)
lapply(dfList,dim)

```
Now we merge the orignal rec and resp datasets with the responders from reminder1 and reminder2 and alumni profile. 

```{r}
#Merge original recipients email with Alumni profile
merged<-merge(orig_email_rec,alumni_profile,by.x="Supporter.ID",by.y="Constituent.UUID",all.x=TRUE)

#Merge with the original email response
merged<-merge(merged,orig_email_resp[,c("Supporter.ID","Orig_email_conversion_date","orig_email_amount","donated_after_orig_email")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Merge with the first reminder response
merged<-merge(merged,reminder1_rec_subset,by="Supporter.ID",all.x=TRUE)

merged<-merge(merged,reminder1_resp[,c("Supporter.ID","reminder1_conversion_date","reminder1_amount","donated_after_reminder1")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Merge with the second reminder response
merged<-merge(merged,reminder2_rec_subset,by="Supporter.ID",all.x=TRUE)

merged<-merge(merged,reminder2_resp[,c("Supporter.ID","reminder2_conversion_date","reminder2_amount","donated_after_reminder2")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Set NA's in indicators to 0
merged[(is.na(merged$donated_after_orig_email)),]$donated_after_orig_email=0
merged[(is.na(merged$donated_after_reminder1)),]$donated_after_reminder1=0
merged[(is.na(merged$donated_after_reminder2)),]$donated_after_reminder2=0

#Adding indicator for donated this year before treatment
merged$donated_TY_pre_treatment <- as.Date("1900-01-01")
merged[!is.na(merged$Last.Gift.Date),]$donated_TY_pre_treatment <- as.Date(merged[!is.na(merged$Last.Gift.Date),]$Last.Gift.Date,"%m/%d/%Y")
#Changed this to exclude donations after the original email was sent, assuming this is for 2a. So now no one has donated before the original email in this calendar year
merged$donated_TY_pre_treatment <- ifelse(merged$donated_TY_pre_treatment>as.Date("2017-12-31") & merged$donated_TY_pre_treatment<as.Date("2017-07-25") ,1,0)
print("Number of donations this year pre-treatment: ")
print(sum(merged$donated_TY_pre_treatment))
```

Let us create dependant and covariates

```{r}
#Check for MULTIPLE DONATIONS

#Define treatment indicator
merged$treat<-ifelse(merged$Split.Name %in% c("Split A"),1,0)
table(merged$Split.Name,merged$treat)

#Total donation amount
merged$orig_email_amount_copy=merged$orig_email_amount
merged$reminder1_amount_copy=merged$reminder1_amount
merged$reminder2_amount_copy=merged$reminder2_amount

merged$orig_email_amount=ifelse(is.na(merged$orig_email_amount_copy),0,merged$orig_email_amount)
merged$reminder1_amount=ifelse(is.na(merged$reminder1_amount_copy),0,merged$reminder1_amount_copy)
merged$reminder2_amount=ifelse(is.na(merged$reminder2_amount_copy),0,merged$reminder2_amount_copy)

merged$total_donation_amount=merged$orig_email_amount+merged$reminder1_amount+merged$reminder2_amount
summary(merged$total_donation_amount)
summary(merged$orig_email_amount)
summary(merged$reminder1_amount)
summary(merged$reminder2_amount)

#Days till donation
merged$donation_date=coalesce(as.Date(merged$Orig_email_conversion_date),as.Date(merged$reminder1_conversion_date),as.Date(merged$reminder2_conversion_date))
#merged[(is.na(merged$donation_date)),]$donation_date=as.Date('2018-7-24')
merged$days_till_donation=merged$donation_date-as.Date(merged$Time.Sent)
#merged[(merged$donation_date>0),]
table(merged$days_till_donation)

#Donation response indicator
merged$donated_any_time=0
merged[!is.na(merged$days_till_donation),]$donated_any_time=1

#OPened any reminder
merged$opened_atleast_one_reminder=merged$opened_reminder1 * merged$opened_reminder2
merged$opened_any_email=merged$opened_orig_email * merged$opened_atleast_one_reminder

#PGSS year based
merged$Ben_involved_ind=ifelse(merged$PGSS.Year>=1997,1,0)
merged$Ben_involved_ind[merged$PGSS.Year==1998]=0
#table(merged$Ben_involved_ind,merged$PGSS.Year)

#Batch age indicator
merged$PGSS_age=merged$PGSS.Year-1982

#Older batch indicator
merged$PGSS_age_bucket=merged$PGSS_age%/%5
merged$PGSS_age_bucket[merged$PGSS.Year>=2007]=6
#table(merged$PGSS.Year,merged$PGSS_age_bucket)


#Interaction of split and Ben involvement
merged$treat_Ben_inter=merged$treat * merged$Ben_involved_ind 
merged$treat_reminder=merged$treat * merged$opened_reminder1 * merged$opened_reminder2

#What else do we need interaction or difference in difference for
```


```{r}

#Define non-compliance. What about people who opened but did not click or contribute?

#Check for emails that were read within the experiment time period: DO we need to stop looking for donations after 8/1? If they opened the final reminder prior to end of the treatment, isn't that enough? This actually depends on the definition of the treatment.
merged1<-merged[(merged$opened_reminder2>as.Date("2017-08-02") ),]
nrow(merged1)

#Method1: Exclude anyone who did not open original email (message is the treatment)
merged$compliant_orig=0
merged[merged$opened_orig_email,]$compliant_orig=1
compliant_orig<-merged[merged$compliant_orig==1,]

#Method2: Subject line is the treatment so everyone is treated
merged$compliant_all=1

#Check number of people who typically do not open emails in previous campaigns

```

Stats

```{r}

cat("Response rate after original email")
table(merged$donated_after_orig_email,merged$treat)

cat("Response rate after reminder1")
table(merged$donated_after_reminder1,merged$treat)

cat("Response rate after reminder2")
table(merged$donated_after_reminder2,merged$treat)

table(merged$opened_orig_email,merged$donated_after_reminder1)

table(merged$opened_orig_email,merged$donated_after_reminder2)

```

Checking for bad control: Does not seem like the reminders are bad control

```{r}
#table(merged$opened_orig_email,merged$opened_reminder1)

#Regress reminder against original email

reg_remember_treatment<-lm(opened_reminder1~merged$Split.Name,data=merged)
print(summary(reg_remember_treatment))

reg_remember_treatment<-lm(opened_reminder2~merged$Split.Name,data=merged)
print(summary(reg_remember_treatment))

reg_remember_treatment<-lm(opened_atleast_one_reminder~merged$Split.Name,data=merged)
print(summary(reg_remember_treatment))

```

Regression for response

```{r}
#names(merged)
```

```{r}
library(lmtest)
library(sandwich)
#Function to return robust errors
printrobustSE <- function(regmodel)
  { 
  regmodel$vcovHC <- vcovHC(regmodel) 
  summ <- coeftest(regmodel, regmodel$vcovHC)    
  return(summ) 
}
```

#Run

```{r}
merged$donated_any_time <- factor(merged$donated_any_time)


#Method1: exclude everyone who did not open original email
reg_response<-glm(donated_any_time~treat+opened_atleast_one_reminder+PGSS_age+last_gift_amount+treat_Ben_inter+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=compliant_orig,family="binomial")
print(summary(reg_response))

#Methods: all
#THis is intent to treat
reg_response<-glm(donated_any_time~treat+opened_atleast_one_reminder+PGSS_age+last_gift_amount+treat_Ben_inter+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=merged,family="binomial")
print(printrobustSE(reg_response))


```

Regression on donation amount
```{r}


#Method1: exclude everyone who did not open original email
reg_amt<-lm(total_donation_amount~treat+opened_atleast_one_reminder+PGSS_age+last_gift_amount+treat_Ben_inter+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=compliant_orig)
print(summary(reg_amt))

#Methods: all
#THis is intent to treat
reg_amt<-lm(total_donation_amount~treat+opened_atleast_one_reminder+PGSS_age+last_gift_amount+treat_Ben_inter+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=merged)
print(summary(reg_amt))

```

Regression for effect of original resposne
```{r}
#Add other regressions here

#Determining effect of two different splits on donation after original e-mail
just_msg_effect_immediate<-lm(donated_after_orig_email~Split.Name, data=merged)
print("Original treatment effect on immediate response:")
print(summary(just_msg_effect_immediate))


```

Regression with HTE
```
#Regression for just the treatments and the last donation indicators
reg_last_donate_cat <- lm(donated_after_orig_email~Split.Name+merged$donated_TY_pre_treatment+LYBUNT_indicator+
                           SYBUNT_Indicator+Never_donator, data=merged)
print("Regression of donations in response to first email against donation_TY_pre_treatment,LYBUNT, SYBUNT and Never_donator")
print(summary(reg_last_donate_cat))

#Regression for the treatments and the last donation indicators and treatments/indicators interactions
reg_last_donate_int <- lm(donated_after_orig_email~Split.Name+donated_TY_pre_treatment+LYBUNT_indicator+
                           SYBUNT_Indicator+Never_donator+
                           Split.Name*donated_TY_pre_treatment+Split.Name*LYBUNT_indicator+Split.Name*SYBUNT_Indicator+
                           Split.Name*Never_donator, data=merged)
print("Regression of treatments and last donation indicators as well as interactions")
print(summary(reg_last_donate_int))


```

Regression on donation delay
```{r}
reg_delay<-lm(days_till_donation~treat+treat_reminder+opened_reminder1+opened_reminder2+PGSS.Year+Months_since_last_donation+last_gift_amount, data=merged2)
#print(summary(reg_delay))

sum(merged$total_donation_amount)

```

Calculate ITT


