---
title: "W241_Project_PGSS_Campaign"
author: "Subha Vadakkumkoor, Walter Burge"
date: "August 3, 2018"
output: pdf_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}
library(data.table)
library(stargazer)
library(dplyr)
library(readr)
```

## Loading data

Data imported from Salsa, excluding PII fields (name and email address) are read into R dataframes. All dataframes have the same structure and format. With each step of the treatment (Orignal email, Reminder1 and Reminder2), there are 2 files: list of people that were assigned the treatment (recieved the email) and list of people that responded to the treatment (donated money).


```{r}

#Load data

#Original email
orig_email_rec<-read.csv('./data/BlastReport_Class Experiment Final Email_Recipients.csv')
setnames(orig_email_rec, old=c("Opened"), new=c("opened_orig_email"))

orig_email_resp<-read.csv('./data/BlastReport_Class Experiment Final Email_Conversions.csv')
sapply(orig_email_resp, class)
#Create an indicator and rename columns to reflect original email response (useful for merge later)
orig_email_resp$donated_after_orig_email=1
names(orig_email_resp)
setnames(orig_email_resp, old=c("Conversion.Date","Amount"), new=c("Orig_email_conversion_date", "orig_email_amount"))

#Reminder1
reminder1_rec<-read.csv('./data/BlastReport_Class experiment Reminder1_Recipients.csv')
setnames(reminder1_rec, old=c("Opened"), new=c("opened_reminder1"))
reminder1_rec_subset=reminder1_rec[,c("opened_reminder1","Supporter.ID")]
```

```{r}
reminder1_resp<-read.csv('./data/BlastReport_Class experiment Reminder1_Conversions.csv')
reminder1_resp$donated_after_reminder1=1
setnames(reminder1_resp, old=c("Conversion.Date","Amount"), new=c("reminder1_conversion_date", "reminder1_amount"))

#Reminder2
reminder2_rec<-read.csv('./data/BlastReport_Class Experiment Reminder 2_Recipients.csv')
setnames(reminder2_rec, old=c("Opened"), new=c("opened_reminder2"))
reminder2_rec_subset=reminder2_rec[,c("opened_reminder2","Supporter.ID")]


reminder2_resp<-read.csv('./data/BlastReport_Class Experiment Reminder 2_Conversions.csv')
reminder2_resp$donated_after_reminder2=1
setnames(reminder2_resp, old=c("Conversion.Date","Amount"), new=c("reminder2_conversion_date", "reminder2_amount"))

#Load donor profile file
alumni_profile<-read.csv('./data/Alumni_profile_all.csv',colClasses = c("character","character","numeric","character","character","character","character","character","character","character","character","numeric","numeric","numeric","numeric","numeric","numeric","numeric"), na.strings=c('','  ','   '))
sapply(alumni_profile,class)
names(alumni_profile)

#Examine the layout of a representative file
cat("Fields in recipients file\n")
names(orig_email_rec)

cat("\nFields in responder files\n")
names(orig_email_resp)

#Get dimensions of each file
cat("\nDimensions of each file\n")
dfList <- list(orig_email_rec,orig_email_resp,reminder1_rec,reminder1_resp,reminder2_rec,reminder2_resp)
lapply(dfList,dim)

```
Now we merge the orignal rec and resp datasets with the responders from reminder1 and reminder2. We assume that the reminders were sent to same people that original emails were sent to. Some of the fields like "opened", etc of reminders are not captured as they may not be required just yet and can be added later if needed.  

```{r}
#Merge original recipients email with Alumni profile
names(alumni_profile)
merged<-merge(orig_email_rec,alumni_profile,by.x="Supporter.ID",by.y="Constituent.UUID",all.x=TRUE)

#Merge with the original email response
merged<-merge(merged,orig_email_resp[,c("Supporter.ID","Orig_email_conversion_date","orig_email_amount","donated_after_orig_email")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Merge with the first reminder response
merged<-merge(merged,reminder1_rec_subset,by="Supporter.ID",all.x=TRUE)

merged<-merge(merged,reminder1_resp[,c("Supporter.ID","reminder1_conversion_date","reminder1_amount","donated_after_reminder1")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Merge with the second reminder response
merged<-merge(merged,reminder2_rec_subset,by="Supporter.ID",all.x=TRUE)

merged<-merge(merged,reminder2_resp[,c("Supporter.ID","reminder2_conversion_date","reminder2_amount","donated_after_reminder2")],by="Supporter.ID",all.x=TRUE)

cat("\nNum of rows",nrow(merged))

#Set NA's in indicators to 0
merged[(is.na(merged$donated_after_orig_email)),]$donated_after_orig_email=0
merged[(is.na(merged$donated_after_reminder1)),]$donated_after_reminder1=0
merged[(is.na(merged$donated_after_reminder2)),]$donated_after_reminder2=0


      
```

Let us create dependant and covariates

```{r}
#Check for MULTIPLE DONATIONS

#Define treatment indicator
merged$treat<-ifelse(merged$Split.Name %in% c("Split A"),1,0)
table(merged$Split.Name,merged$treat)

#Total donation amount
merged$orig_email_amount_copy=merged$orig_email_amount
merged$reminder1_amount_copy=merged$reminder1_amount
merged$reminder2_amount_copy=merged$reminder2_amount

merged$orig_email_amount=ifelse(is.na(merged$orig_email_amount_copy),0,merged$orig_email_amount)
merged$reminder1_amount=ifelse(is.na(merged$reminder1_amount_copy),0,merged$reminder1_amount_copy)
merged$reminder2_amount=ifelse(is.na(merged$reminder2_amount_copy),0,merged$reminder2_amount_copy)

merged$total_donation_amount=merged$orig_email_amount+merged$reminder1_amount+merged$reminder2_amount
summary(merged$total_donation_amount)
summary(merged$orig_email_amount)
summary(merged$reminder1_amount)
summary(merged$reminder2_amount)



#Days till donation
merged$donation_date=coalesce(as.Date(merged$Orig_email_conversion_date),as.Date(merged$reminder1_conversion_date),as.Date(merged$reminder2_conversion_date))
merged[(is.na(merged$donation_date)),]$donation_date=as.Date('2018-7-24')

merged$days_till_donation=merged$donation_date-as.Date(merged$Time.Sent)
#merged[(merged$donation_date>0),]
table(merged$days_till_donation)

#Donation response indicator
merged$donated_any_time=0
merged[merged$days_till_donation>0,]$donated_any_time=1

#Define non-compliance. What about people who opened but did not click or contribute?

table(merged$opened_orig_email,merged$donated_after_reminder1)
table(merged$opened_orig_email,merged$donated_after_reminder2)

merged$compliant=0
merged[merged$opened_orig_email,]$compliant=1
merged$compliant=ifelse(merged$opened_reminder1,1,0)
merged$compliant=ifelse(merged$opened_reminder2,1,0)
table(merged$opened_reminder1)

#Need to add more indicators : read both original and reminder and responded only after reminder, etc

```

Stats

```{r}

cat("Response rate after original email")
table(merged$donated_after_orig_email,merged$treat)

cat("Response rate after reminder1")
table(merged$donated_after_reminder1,merged$treat)

cat("Response rate after reminder2")
table(merged$donated_after_reminder2,merged$treat)

table(merged$opened_orig_email,merged$donated_after_reminder1)

table(merged$opened_orig_email,merged$donated_after_reminder2)

```

Initial regression trial

```{r}
#names(merged)
merged$treat_reminder=merged$treat * merged$opened_reminder1 * merged$opened_reminder2
merged$opened_atleast_one_reminder=merged$opened_reminder1 * merged$opened_reminder2
#Need to add more covariates
merged$donated_any_time <- factor(merged$donated_any_time)
reg_response<-glm(donated_any_time~treat+opened_atleast_one_reminder+PGSS.Year+last_gift_amount+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=merged,family="binomial")
print(summary(reg_response))
#Add robust errors

names(merged)
```

```{r}
#Add other regressions here

#Determining effect of two different splits on donation after original e-mail
just_msg_effect_immediate<-lm(donated_after_orig_email~Split.Name, data=merged)
print("Original treatment effect on immediate response:")
print(summary(just_msg_effect_immediate))

#Adding indicator for donated this year before treatment
merged$donated_TY_pre_treatment <- as.Date("1900-01-01")
merged[!is.na(merged$Last.Gift.Date),]$donated_TY_pre_treatment <- as.Date(merged[!is.na(merged$Last.Gift.Date),]$Last.Gift.Date,"%m/%d/%Y")
merged$donated_TY_pre_treatment <- ifelse(merged$donated_TY_pre_treatment>as.Date("2017-12-31"),1,0)
print("Number of donations this year pre-treatment: ")
print(sum(merged$donated_TY_pre_treatment))

#Regression for just the treatments and the last donation indicators
reg_last_donate_cat <- lm(donated_after_orig_email~Split.Name+merged$donated_TY_pre_treatment+LYBUNT_indicator+
                            SYBUNT_Indicator+Never_donator, data=merged)
print("Regression of donations in response to first email against donation_TY_pre_treatment,LYBUNT, SYBUNT and Never_donator")
print(summary(reg_last_donate_cat))

#Regression for the treatments and the last donation indicators and treatments/indicators interactions
reg_last_donate_int <- lm(donated_after_orig_email~Split.Name+donated_TY_pre_treatment+LYBUNT_indicator+
                            SYBUNT_Indicator+Never_donator+
                            Split.Name*donated_TY_pre_treatment+Split.Name*LYBUNT_indicator+Split.Name*SYBUNT_Indicator+
                            Split.Name*Never_donator, data=merged)
print("Regression of treatments and last donation indicators as well as interactions")
print(summary(reg_last_donate_int))

#Need to add more covariates
merged2<-merged[merged$total_donation_amount>0, ]
summary(merged$total_donation_amount)

reg_amount<-lm(total_donation_amount~treat+opened_atleast_one_reminder+PGSS.Year+last_gift_amount+SYBUNT_Indicator+LYBUNT_indicator+gift_count, data=merged2)
print(summary(reg_amount))

```

```{r}
reg_delay<-lm(days_till_donation~treat+treat_reminder+opened_reminder1+opened_reminder2+PGSS.Year+Months_since_last_donation+last_gift_amount, data=merged2)
#print(summary(reg_delay))

sum(merged$total_donation_amount)

```

```{r}
table(merged$opened_orig_email,merged$opened_reminder1)
```

